Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-21 paper/paper.tex
Change Intro part

\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities for sensing and energy applications. The
reduction of characteristic dimensions in nanofluidics gives rise to
substantially different transport properties compared to their bulk
counterparts \cite{Schoch_2008}. In nanopores, for example, the effect
of surface-mediated transport becomes dominant when the pore size is
comparable to the solute diffusion length, enabling new applications,
including ionic diodes \cite{Karnik_2007}, field-effect transistors
\cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
atomically thin two-dimensional (2D) materials, such as graphene,
embody an ideal membrane materials due to their ultimate permeability
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as the
desalination membrane enables excellent salt rejection by preventing
the permeation of the hydrated ions the (1 nm - 3 nm) with
simultaneous high water permeation
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
the fabrication of sub-5 nanometer porous 2D membranes over a large
area with atomic precision is technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of large pores can significantly diminish salt rejection.
Accordingly, recent research efforts have explored the effect of
surface charges on the selectivity of ion transport, as a consequence
of coulombic repulsion of the solvated ion and the charged functional
groups on graphene \cite{Rollings_2016,Surwade_2014}. However, it
remains controversial that if the surface charges can result in a
degree of salt rejection, as the membrane potential is sensitive to
the surroundings and chemical treatment \cite{Li_2008}. The
difficulty in turn hinders fundamental understanding of the
interactions between the atomically thin 2D membrane and electrolyte
solution. Here, we demonstrate macroscopic salt rejection through a
sheet of large-area porous graphene using electrostatic gating,
thereby deepening the understanding of ion-graphene interaction and
its implications on nanoporous graphene-based desalination
applications.

>>>>

\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties compared to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the solute diffusion length, enabling new applications,
including ionic diodes \cite{Karnik_2007}, field-effect transistors
\cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to their ultimate
permeability
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as the
desalination membrane enables excellent salt rejection by preventing
the permeation of hydrated ions with a high water permeability
simultaneous
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
the fabrication of subnanometer porous 2D membranes over a large area
with atomic precision remains technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of large pores can significantly diminish salt rejection.
Very recently, a number of reports have explored the effect of surface
charges on the selectivity of ion transport through graphene
nanopores, as a consequence of the electrostatic interactions between
solvated ions and the charged functional groups attached on graphene
\cite{Rollings_2016,Surwade_2014}. However, it remains controversial
that if the surface charges can result in a degree of salt rejection,
as the membrane charge and potential cannot be precisely quantified
and are sensitive to the surroundings and chemical treatment
\cite{Li_2008}. The difficulty in turn hinders fundamental
understanding of the interactions between the atomically thin 2D
membrane and electrolyte solution. Here, we demonstrate macroscopic
salt rejection through a sheet of large-area porous graphene using
electrostatic gating, thereby deepening the understanding of
ion-graphene interaction and its implications on nanoporous
graphene-based desalination applications.
